Dominance Regions for Imaginary $\bfg$-vectors

### 2020-07-12 dominance_regions.tex
Random edits in section 3

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}

@@

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge 4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.

@@

  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \end{lemma}
  \begin{proof}
    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require that 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
    or
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
    As these represent the same relation, the result follows.
  \end{proof}

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
  \begin{lemma}
    The vectors $(2b, -bc+\sqrt{bc(bc-4)})$ (resp. $(2b, -bc-\sqrt{bc(bc-4)})$) and $(2c, bc+\sqrt{bc(bc-4)})$ (resp. $(2c, bc-\sqrt{bc(bc-4)})$) are perpendicular.
  \end{lemma}
  \begin{proof}
    This is immediate from the equality $(-bc+\sqrt{bc(bc-4)})(bc+\sqrt{bc(bc-4)})=-4bc$.
  \end{proof}
  \begin{lemma}
    \label{le:imaginary stability}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
  \end{lemma}
  \begin{proof}
    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$ respectively.
    The claim is immediate for $\phi_{t_2}$ since the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$ are eigenvectors.
    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows.
  \end{proof}

@@

  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
  This leads to the following more general recursive structure.
  \begin{lemma}
    For $i,j\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+j,\varepsilon}=\begin{cases} u_{j+1,\varepsilon}u_{i,-\varepsilon}-u_{j,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i,\varepsilon}-u_{j,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the cases $j=0,1$ being tautological and reproducing the defining recursion respectively.
    Using the claim for $j>0$ and then the defining recursion twice, we get
    \begin{align*}
      u_{i+j+1,\varepsilon}&=\begin{cases} u_{j+1,\varepsilon}u_{i+1,-\varepsilon}-u_{j,-\varepsilon}u_{i,\varepsilon} & \text{if $j$ is odd;}\\ u_{j+1,-\varepsilon}u_{i+1,\varepsilon}-u_{j,\varepsilon}u_{i,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
      &=\begin{cases} (u_{2,-\varepsilon}u_{j+1,\varepsilon}-u_{j,-\varepsilon})u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j$ is odd;}\\ (u_{2,\varepsilon}u_{j+1,-\varepsilon}-u_{j,\varepsilon})u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j$ is even;} \end{cases}\\
      &=\begin{cases} u_{j+2,-\varepsilon}u_{i,\varepsilon}-u_{j+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $j+1$ is even;}\\ u_{j+2,\varepsilon}u_{i,-\varepsilon}-u_{j+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $j+1$ is odd;} \end{cases}
    \end{align*}
    which is the claimed recursion for $j+1$.
    These calculations can be reverses to show the result for $j<0$.
  \end{proof}

  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
    and so
    \begin{align*}
      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2)
    \end{align*}
    where the last equality uses \eqref{eq:long Chebyshev recursion}.

    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
  \end{proof}

@@

    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (b) for $k+1$
    .
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.

>>>>

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\usepackage[bookmarks=true, bookmarksopen=true, bookmarksdepth=3,bookmarksopenlevel=2, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, menucolor=blue, urlcolor=blue]{hyperref}

@@

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge 4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Here we may take $\TT_2$ to have vertices labelled $t_i$ for $i\in\ZZ$, with $t_{2j}$ joined to $t_{2j+1}$ by an edge labelled $1$ and $t_{2j-1}$ joined to $t_{2j}$ by an edge labelled $2$.
  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC_{t_i}(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.

@@

  By an eigenvector of a piecewise-linear map $\phi$, we mean a vector $\lambda$ such that for each $k\ge0$, there exists a scalar $\nu_k$ so that $\phi^k(\lambda)=\nu_k\lambda$.
  \begin{lemma}
    Any nonzero eigenvector of $\phi_{t_2}$ is a positive multiple of one of the vectors $\big(2b,-bc\pm\sqrt{bc(bc-4)}\big)$.
  \end{lemma}
  \begin{proof}
    First observe that the equation $\phi_{t_2}^k(\lambda)=\nu_k\lambda$ cannot be satisfied for all $k\ge0$ unless $\lambda_1\ge 0$ and $c\lambda_1+\lambda_2\ge 0$.
    In this region, $\phi_{t_2}$ is linear with eigenvalue $\nu$ satisfying $\nu^2-(bc-2)\nu+1=0$, i.e. $\nu=\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}$.
    We thus require that 
    \[\frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_1=(bc-1)\lambda_1+b\lambda_2 \qquad\text{and}\qquad \frac{bc-2\pm\sqrt{bc(bc-4)}}{2}\lambda_2= -c\lambda_1-\lambda_2,\]
    or
    \[\frac{-bc\pm\sqrt{bc(bc-4)}}{2b}\lambda_1=\lambda_2 \qquad\text{and}\qquad \frac{-bc\mp\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1.\]
    As these represent the same relation, the result immediately follows by inspection.
  \end{proof}

  Write $\cI \subset \RR^2$ for the \emph{imaginary cone} (positively) spanned by the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$.
  Also, write $\cI' \subset \RR^2$ for the \emph{dual imaginary cone} (positively) spanned by the vectors $(-bc\pm\sqrt{bc(bc-4)},2c)$.
  \begin{lemma}
    The vectors $(2b, -bc+\sqrt{bc(bc-4)})$ (resp. $(2b, -bc-\sqrt{bc(bc-4)})$) and $(2c, bc+\sqrt{bc(bc-4)})$ (resp. $(2c, bc-\sqrt{bc(bc-4)})$) are perpendicular.
  \end{lemma}
  \begin{proof}
    This is immediate from the equality $(-bc+\sqrt{bc(bc-4)})(bc+\sqrt{bc(bc-4)})=-4bc$.
  \end{proof}
  \begin{lemma}
    \label{le:imaginary stability}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have $\phi_{t_{2j}}(\lambda)\in\cI$ and $\phi_{t_{2j+1}}(\lambda)\in\cI'$.
  \end{lemma}
  \begin{proof}
    Note that $\phi_{t_{2j}}=\phi_{t_2}^j$ and $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ so the result follows from the cases $j=1$ and $j=0$ respectively.
    The claim is immediate for $\phi_{t_2}$ since the vectors $(2b,-bc\pm\sqrt{bc(bc-4)})$ are eigenvectors.
    Now, we have $\phi_{t_1}(\lambda)=(-\lambda_1,c\lambda_1+\lambda_2)$ and so $\phi_{t_1}\big( (2b,-bc\pm\sqrt{bc(bc-4)}) \big)=(-2b,bc\pm\sqrt{bc(bc-4)})$, which is the $\frac{bc\pm\sqrt{bc(bc-4)}}{2c}$-multiple of the boundary vector for $\cI'$ and the result follows for arbitrary $\lambda\in\cI$ by linearity.
  \end{proof}

@@

  The recursion can be written more succinctly as $u_{i+1,\varepsilon}=u_{2,\varepsilon}u_{i,-\varepsilon}-u_{i-1,\varepsilon}$ with the additional initial condition $u_{2,\varepsilon}=\begin{cases} b & \text{if $\varepsilon=+$;}\\ c & \text{if $\varepsilon=-$.} \end{cases}$
  This leads to the following more general recursive structure.
  \begin{lemma}
    For $i,\ell\in\ZZ$ and $\varepsilon\in\{\pm\}$, we have
    \begin{equation}
      \label{eq:long Chebyshev recursion}
      u_{i+\ell,\varepsilon}=\begin{cases} u_{\ell+1,\varepsilon}u_{i,-\varepsilon}-u_{\ell,-\varepsilon}u_{i-1,\varepsilon} & \text{\upshape if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i,\varepsilon}-u_{\ell,\varepsilon}u_{i-1,-\varepsilon} & \text{\upshape if $\ell$ is even.} \end{cases}
    \end{equation}
  \end{lemma}
  \begin{proof}
    We work by induction on $\ell$, the cases $\ell=0,1$ being tautological and reproducing the defining recursion respectively.
    Using the claim for $j>0$ and then the defining recursion twice, we get
    \begin{align*}
      u_{i+\ell+1,\varepsilon}&=\begin{cases} u_{\ell+1,\varepsilon}u_{i+1,-\varepsilon}-u_{\ell,-\varepsilon}u_{i,\varepsilon} & \text{if $\ell$ is odd;}\\ u_{\ell+1,-\varepsilon}u_{i+1,\varepsilon}-u_{\ell,\varepsilon}u_{i,-\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
      &=\begin{cases} (u_{2,-\varepsilon}u_{\ell+1,\varepsilon}-u_{\ell,-\varepsilon})u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell$ is odd;}\\ (u_{2,\varepsilon}u_{\ell+1,-\varepsilon}-u_{\ell,\varepsilon})u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell$ is even;} \end{cases}\\
      &=\begin{cases} u_{\ell+2,-\varepsilon}u_{i,\varepsilon}-u_{\ell+1,\varepsilon}u_{i-1,-\varepsilon} & \text{if $\ell+1$ is even;}\\ u_{\ell+2,\varepsilon}u_{i,-\varepsilon}-u_{\ell+1,-\varepsilon}u_{i-1,\varepsilon} & \text{if $\ell+1$ is odd;} \end{cases}
    \end{align*}
    which is the claimed recursion for $\ell+1$.
    These calculations can be reversed to show the result for $\ell<0$.
  \end{proof}

  \begin{lemma}
    \label{le:imaginary transformations}
    For $j\in\ZZ$ and $\lambda\in\cI$, we have
    \begin{align*}
      \phi_{t_{2j}}(\lambda)&=(u_{2j+1,+}\lambda_1+u_{2j,+}\lambda_2,-u_{2j,-}\lambda_1-u_{2j-1,-}\lambda_2);\\
      \phi_{t_{2j+1}}(\lambda)&=(-u_{2j+1,+}\lambda_1-u_{2j,+}\lambda_2,u_{2j+2,-}\lambda_1+u_{2j+1,-}\lambda_2).
    \end{align*}
  \end{lemma}
  \begin{proof}
    We work by induction on $j$, the case $j=0$ being clear from the definitions.
    As observed above, we have $\phi_{t_{2j}}=\phi_{t_2}^j$.
    For $\lambda\in\cI$, the action of $\phi_{t_2}$ from \eqref{eq:forward two step mutation} can be rewritten as
    \[\phi_{t_2}(\lambda)=(u_{3,-}\lambda_1+u_{2,+}\lambda_2,-u_{2,-}\lambda_1-u_{1,+}\lambda_2),\]
    and so
    \begin{align*}
      \phi_{t_{2j+2}(\lambda)}&=\phi_{t_2}\phi_{t_{2j}}(\lambda)\\
      &=\big( (u_{3,-}u_{2j+1,+}-u_{2,+}u_{2j,-})\lambda_1+(u_{3,-}u_{2j,+}-u_{2,+}u_{2j-1,-})\lambda_2,\\
      &\qquad -(u_{2,-}u_{2j+1,+}-u_{1,+}u_{2j,-})\lambda_1-(u_{2,-}u_{2j,+}-u_{1,+}u_{2j-1,-})\lambda_2 \big)\\
      &=(u_{2j+3,+}\lambda_1+u_{2j+2,+}\lambda_2, -u_{2j+2,-}\lambda_1-u_{2j+1,-}\lambda_2),
    \end{align*}
    where the last equality uses \eqref{eq:long Chebyshev recursion} with $i=2j+1$ and $\ell=2$.

    Similarly, using $\phi_{t_1}(\lambda)=(-\lambda_1,u_{2,-}\lambda_1+u_{1,+}\lambda_2)$ for $\lambda\in\cI$, together with the basic Chebyshev recursion and the equality $\phi_{2j+1}=\phi_{t_1}\phi_{t_2}^j$ gives the claimed formula for $\phi_{t_{2j+1}}$ from that of $\phi_{t_{2j}}$.
  \end{proof}

@@

    Assuming the inequalities (a)-(d) hold for $k$, we apply Lemma~\ref{le:transformed inequalities} with $\phi_{t_2}^{-1}$.
    Both of the boundary rays corresponding to the inequalities (a) and (d) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & -b\\ c & bc-1 \end{array}\right]$, also the boundary segment corresponding to (b) intersects this region.
    Thus applying Lemma~\ref{le:transformed inequalities} to (a) gives the inequality 
    \[u_{2k+2,-}x+u_{2k+1,+}y=(u_{3,+}u_{2k,-}-u_{2,-}u_{2k-1,+})x+(u_{2,+}u_{2k,-}-u_{1,-}u_{2k-1,+})y\le u_{i,-}\lambda_1+u_{i-1,+}\lambda_2,\]
    which is the inequality (a) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}; while applying this to (d) gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y=(-u_{3,+}u_{2k-1,-}+u_{2,-}u_{2k-2,+})x+(-u_{2,+}u_{2k-1,-}+u_{1,-}u_{2k-2,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ again by Lemma~\ref{eq:long Chebyshev recursion}; finally applying this to (b) gives the inequality 
    \[u_{2k+3,-}x+u_{2k+2,+}y=(u_{3,+}u_{2k+1,-}-u_{2,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (b) for $k+1$
    .
    Similarly, the boundary segment corresponding to (c) lies entirely in the region where $\phi_{t_2}^{-1}$ acts according to the matrix $\left[ \begin{array}{cc} -1 & 0\\ c & -1 \end{array}\right]$.
    Thus applying Lemma~\ref{le:transformed inequalities} to (c) gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y=(u_{1,+}u_{2k-1,-}-u_{2,-}u_{2k,+})x+(-u_{0,+}u_{2k-1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (d) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, in particular we see that the segment determined by (c) and the ray determined by (d) align in the image.
    Lastly, the boundary segment corresponding to (b) also intersects the regions where $\phi_{t_2}^{-1}$ acts according to the matrices $\left[ \begin{array}{cc} -1 & -b\\ 0 & -1 \end{array}\right]$ and $\left[ \begin{array}{cc} -1 & 0\\ 0 & -1 \end{array}\right]$ respectively.
    Applying Lemma~\ref{le:transformed inequalities} to (b) with the first matrix gives the inequality 
    \[-u_{2k+1,-}x+u_{2k+2,+}y=(-u_{1,+}u_{2k+1,-}+u_{0,-}u_{2k,+})x+(u_{2,+}u_{2k+1,-}-u_{1,-}u_{2k,+})y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which is the inequality (c) for $k+1$ by Lemma~\ref{eq:long Chebyshev recursion}, while applying Lemma~\ref{le:transformed inequalities} to (b) with the second matrix gives the inequality 
    \[-u_{2k+1,-}x-u_{2k,+}y\le u_{i+1,-}\lambda_1+u_{i,+}\lambda_2,\]
    which again reproduces the inequality (d) and aligns with the previous segment and ray in the image.
    This completes the induction on $k$, proving the Claim and the result for $i$ even.
